---
title: "Test automarking"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(testthat)
library(lintr)

```

## Question1: Aim

Save time. Create a function called text_shortener that will drastically shorten a written text. Specifically, we want it to:

  * replace multiple consecutive spaces by a single space.
  * abbreviate any word that is longer than 5 characters (i.e. replace the additional characters by a '.').
  * remove all of the following words: "the", "really", "truly", "very".
  * keep only the first sentence in every paragraph.


## Question 1 : Autotesting

Using the `testthat` package, I run 13 tests (complete code for this is available elsewhere). Below, only the FAILED tests are reported.

```{r question1_tests}

source("question1.R")
test_results <- test_file(path     = "../../src/question1_testcode.R",
	      	          reporter = CheckReporter)

```

### Question 1: Lint syntax / style guide checking

As covered in class, we fuse lint to ensure that best practices are being respected.

```{r question1_lint}

lint_issues <-lint(filename = "question1.R",
	           linters  = with_defaults(line_length_linter(120)))
lint_issues
length(lint_issues)
```
