---
title: "Automarking"
output: html_document
author: Yannick Wurm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(testthat)
library(lintr)
library(stringi); library(stopwords); library(stringr); library(rmarkdown); library(tm); library(tokenizers);
student_id <- gsub(x = getwd(), pattern = ".*/", replacement = "")
```


This is run for student `r student_id` on `r format(Sys.time(), "%A %B %d, %Y")` at `r format(Sys.time(), "%H:%M:%S")`.

## Context: Text shortener function

Save time. Create a function called text_shortener that will drastically shorten a written text. Specifically, we want it to:

  * replace multiple consecutive spaces by a single space.
  * abbreviate any word that is longer than 5 characters (i.e. replace the additional characters by a '.').
  * remove all of the following words: "the", "really", "truly", "very".
  * keep only the first sentence in every paragraph.
  * we do not want anything printed on the screen - the shortened text should simply be "returned"


## Loading your file


```{r loading, echo = FALSE}
r_files <- grep(x = list.files(), pattern = ".R$", value = TRUE)

submitted_script <- grep(x = r_files, pattern = "test_text_shortener.R", value = TRUE, invert = TRUE)

source(submitted_script)
```

Evaluating `r submitted_script`

```{r load2, echo=FALSE, eval=TRUE}
if (file.exists("additional_notes.txt")) {
  cat(readLines("additional_notes.txt"), sep = "\n")
} else {
  # no problems loading
}
```

Your `text_shortener()` function was: 

```{r, code = text_shortener, eval = FALSE}
```



## Autotesting

Using the `testthat` package, I run automated tests for each of the features we request (complete code for this is available elsewhere). 

```{r tests, echo = FALSE, include = FALSE}
test_results <- test_file(path     = "test_text_shortener.R")
```

I performed `r sum(data.frame(test_results)$nb)` tests. Among these, `r sum(data.frame(test_results)$failed)` were unsuccessful.

### The complete series of tests are: 

```{r code = readLines("test_text_shortener.R"), eval = FALSE}
```

### Output: 
Below, only the FAILED tests are reported. 

```{r rerunning_with_output}
test_file(path     = "test_text_shortener.R")
```

### Lint syntax / style guide checking

As covered in class, we use `lintr` to ensure that formatting is inline with the style guide. 

```{r question1_lint, echo = FALSE}
                                                                                                 
r_files <- grep(x = list.files(), pattern = ".R$", value = TRUE)                                                                                                                                        
                                                                                                                                                                                                        
submitted_script <- grep(x = r_files, pattern = "test_text_shortener.R", value = TRUE, invert = TRUE)    


lint_issues <- lint(filename = submitted_script,
                    linters  = with_defaults(line_length_linter(100)))
```

Overall, `lintr` found `r length(lint_issues)` issues with style of your code.

#### Output:

The identified issues are listed below:

```{r echo = TRUE}
lint_issues
```

