---
title: "Automarking for 25% of Bio773p Coursework"
output: html_document
author: Yannick Wurm
---

<style>
pre, code {
  font-family: Consolas, Monaco, "Courier New", Courier, monospace;
  font-size: 0.75em;
  padding: 3px;
  border-radius: 5px;
  overflow-x: auto;         /* Horizontal scrolling */
  white-space: pre-wrap;    /* Wrap long lines */
}
h2 {
  font-size: 1.5em;
}
h3 {
  font-size: 1.2em;
}
body {
  font-family: Arial, sans-serif;
  line-height: 1.6;
  margin: 0 auto;
  padding: 20px;
  max-width: 800px;
  background-color: #f9f9f9;
  color: #333;
}
h1, h2, h3 {
  color: #00A6FB; /* Bright Electric Blue */
  border-bottom: 2px solid #1C5D99; /* Subtle underline */
  padding-bottom: 5px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(testthat)
library(lintr)
library(stringi); library(stopwords); library(stringr); library(rmarkdown); library(tm); library(tokenizers);
student_id <- gsub(x = getwd(), pattern = ".*/", replacement = "")
```


This is run for student `r student_id` on `r format(Sys.time(), "%A %B %d, %Y")` at `r format(Sys.time(), "%H:%M:%S")`.


## Introduction

This document provides feedback on the function you submitted for automarking. Below, you'll find detailed results for the automated tests, as well as feedback on code style and formatting.

**Context**: The goal of the assignment was to write a function that takes a text as input and returns a condensed version of that text. The following requirements were specified:

### Function Requirements:

* Consecutive Spaces: The function should identify and replace sequences of multiple spaces in the input text with a single space.
* Word Abbreviation: Any word in the text that has more than 5 characters should be abbreviated. This means retaining the first 5 characters of the word and replacing all subsequent characters with a single period ('.'). For instance, "evolution" becomes "evolu.".
* Word Removal: The function should completely remove specific words from the text. These words are: "the", "really", "truly", "very". They should be removed regardless of their case (i.e., "The" or "tHe" should also be removed).
* Sentence Retention: For every paragraph in the input, only the first sentence should be kept. All other sentences in that paragraph should be discarded. However, the original structure of paragraphs should remain intact. Each retained sentence should stand as its own paragraph in the output.
* Input: The function should take a single character string as input.
* Console Output: The function should not display or print any content to the R console. Instead, the condensed version of the text should be returned as a string.

### Submission Instructions:

* Your solution should be submitted as a single .R file. Ensure that this file can be directly loaded into an R environment without errors.
* The .R file should exclusively contain functions. If there's a need to load any R libraries, incorporate this within a distinct function named setup() inside the same file.
While it's permissible to include auxiliary functions (for instance, for testing or sub-tasks), do not incorporate any standalone R commands or scripts outside of function definitions.
Name your file appropriately, following any conventions provided. Automated Grading: Upon submission, your function will be run through a series of tests to validate its correctness. Ensure that your function meets all the specified requirements to score maximum points.


## Loading your file


```{r loading, echo = FALSE, eval = TRUE}
r_files <- grep(x = list.files(), pattern = ".R$", value = TRUE, ignore.case = TRUE)

submitted_script <- grep(x = r_files, pattern = "test_text_shortener.R", value = TRUE, invert = TRUE)
rm(r_files)

source(submitted_script)

# if shorten_text doesn't exist, look for other functions.
if (!exists("shorten_text")) {
  user_objects <- ls()
  user_objects <- user_objects[!user_objects %in% c("submitted_script", "user_objects", "student_id")]
  message("shorten_text function not found")
  cat(x = paste("\n\nA function named shorten_text unfortunately was not found ",
                "in your submission. We found this instead:", user_objects),
      file ="additional_notes.txt",
      append = TRUE
     )

  if (length(user_objects) == 1) {
    shorten_text <-  environment()[[user_objects]]
  } else {
    cat(x = "\n\nMultiple functions found so I cannot automatically find the right one: ", paste(user_objects, sep=", "),
        file ="additional_notes.txt",
        append = TRUE)
    stop("shorten_text function not found. Need to stop marking.")
  }
}

#  - If just one, use that one (copy it to shorten_text, and put into additional notes)
#  - if more than one print error.
```

### The script, `r submitted_script`, you submitted was:

```{r eval=TRUE, echo=FALSE}
lines <- readLines(submitted_script, warn = FALSE)
knitr::asis_output(paste0("```r\n", paste(lines, collapse = "\n"), "\n```"))
```


### Trying to load `r submitted_script`....

```{r load2, echo=FALSE, eval=TRUE}
if (file.exists("additional_notes.txt")) {
  cat(readLines("additional_notes.txt", warn = FALSE), sep = "\n")
} else {
  message("No problems loading this file")
}
```



## Automated testing of code functionality

Using R's `testthat` package, we run automated tests for each of the requested features. We run these under diverse scenarios.

```{r tests, echo = FALSE, include = FALSE}
test_results <- test_file(path     = "test_text_shortener.R")
```

I performed `r length(data.frame(test_results)$result)` tests of the code functionality. Among these, `r sum(data.frame(test_results)$passed)` passed successfully. **This gives you a base score of `r round(100 *sum(data.frame(test_results)$passed)/length(data.frame(test_results)$result))` out of 100 for the code's functionality**. This mark could be reduced if there were difficulties loading the code, if there were warnings, or if the code did not follow the style guide.

There were `r sum(data.frame(test_results)$warning)` warnings.

### The complete series of automated tests I ran are shown below:

A brief explanation of how to read these automated tests. Each `test_that()` call is a test. The first argument is a description of the test. Thereafter is a call to your function on some test text. The `expected = ` line indicates what I expected as a result when running your function on the test text. If the code returns the expected result, the test passes. If it does not, the test fails.

Some of the tests check for only one particular aspect of what was requested in this exercise (e.g., exclusively checking that excess whitespace is removed). While others check for multiple aspects.

```{r code = readLines("test_text_shortener.R"), eval = FALSE}
```

### Output:

We ran each of the tests outlined above. Here, we see `testthat` output only for the tests that were unsuccessful. For each, you can see:

  * the description of the test that was run (e.g., "Remove all of the following words: 'the', 'really', 'truly', 'very'.")
  * It then provides more details on the comparison it did, what was expected, and what your code. If for many of the tests you see an output like "NULL" or "Lengths differ", then your function likely didn't return a single string. This could for example have happened if you are printing to the console, or if you are returning a vector of strings instead of a single string. Unfortunately, returning a string was one of the essential requirements for this exercise.

```{r rerunning_with_output, echo = FALSE, eval = TRUE}
#a <- test_file(path     = "test_text_shortener.R")
library(testthat)
# Initialize a variable to hold the Markdown output
output <- ""

results <- test_file(path = "test_text_shortener.R", reporter = "List")

for (result in results) {
  evaluation <- as.character((result$results)[[1]])
  if (grepl(pattern = "success", x = evaluation)) {
    # Add success message
    output <- paste0(output, "\n\n### ✅ Test: ", result$test, " (Passed)\n\n")
  } else {
    # Add the test name as a Markdown header
    output <- paste0(output, "\n\n### ❌ Test: ", result$test, "\n\n")
    
    # Split the evaluation message into lines
    lines <- strsplit(evaluation, "\n")[[1]]

    if (length(lines) != 4) {
      # If not 4 lines, display raw evaluation
      formatted_lines <- paste("    ", lines)
      output <- paste0(output, "```\n", paste(formatted_lines, collapse = "\n"), "\n```\n")
    } else {
     # If exactly 4 lines, process the last two
      your_output <- sub("x\\[1\\]:",     "Your output :", lines[3])
      expected_output <- sub("y\\[1\\]:", "Expected    :", lines[4])
      
      # Add formatted outputs directly
      output <- paste0(
        output,
        "```\n", your_output, "\n", expected_output, "\n```\n"
      )
    }
  }
}

# Output the Markdown content
knitr::asis_output(output)
```

## Lint syntax / style guide checking

As covered in class, we use the `lintr` library to check whether formatting is in line with the style guide.

```{r question1_lint, echo = FALSE}

r_files <- grep(x = list.files(), pattern = ".R$", value = TRUE, ignore.case = TRUE)

submitted_script <- grep(x = r_files, pattern = "test_text_shortener.R", value = TRUE, invert = TRUE)


lint_issues <- lint(filename = submitted_script,
                    linters  = linters_with_defaults(line_length_linter(100)))
```

Overall, `lintr` found `r length(lint_issues)` issues with style of your code.

The identified issues are listed below:

```{r echo = FALSE}
# Initialize output variable
lint_output <- ""

# Pretty print each issue - assuming `lint_issues` is a list of issues
for (issue in lint_issues) {
  # Add line number, column number, and message
  lint_output <- paste0(
    lint_output,
    "\n- **Line", issue$line_number, ", column ", issue$column_number, "**: ",
    issue$message, "\n",
    "  - **Line of code:** '`", issue$line, "`'\n"
  )
}

# Output the final Markdown content
knitr::asis_output(paste0("\n### Identified Lint Issues\n\n", lint_output))


